### 2015-09-15 vmcai-2016-tex/intro.tex

Precisely modeling operations on unconstrained heaps
is challenging because it requires formulating logical predicates over
an input domain that contains a potentially unbounded number of hidden
references~\cite{Chen:2013,Qu:2011}. Generalized symbolic execution
(\gsetxt{}), and its variants, provide an accurate
solution, but they quickly produce an overwhelming number of execution
paths for all but the simplest heap shapes \cite{GSE03,Deng:2007}. Other efforts to 
create heap inputs for guarded value set-based analysis 
techniques \cite{Dillig:2011,Xie:2005} have yet to
produce results provably equivalent to~\gsetxt{}. Thus, despite
the advantages of using guarded value sets, it remains an open
question to how they can be used in symbolic execution to automatically
model all possible program behaviors in the case of an arbitrary input
heap.

>>>>

Precisely modeling operations on unconstrained heaps
is challenging because it requires formulating logical predicates over
an input domain that contains a potentially unbounded number of hidden
references~\cite{Chen:2013,Qu:2011}. Generalized symbolic execution
(\gsetxt{}), and its variants, provide an accurate
solution, but they quickly produce an overwhelming number of execution
paths for all but the simplest heap shapes \cite{GSE03,Deng:2007}. Other efforts to 
create heap inputs for guarded value set-based analysis 
techniques  have yet to
produce results provably equivalent to~\gsetxt{} \cite{Dillig:2011,Xie:2005}. Thus, despite
the advantages of using guarded value sets, it remains an open
question to how they can be used in symbolic execution to automatically
model all possible program behaviors in the case of an arbitrary input
heap.

### 2015-09-15 vmcai-2016-tex/rw.tex

%DSE
A number of dynamic symbolic execution (\dsetxt{}) methods use some form 
of symbolic heap representation, including PEX~\cite{Tillmann:2008} and SAGE~\cite{Elkarablieh:2009}. These~\dsetxt{} methods have shown a high degree of utility in practical applications with a wide variety of real-world programs. However, PEX and SAGE use array theories to represent program state instead of guarded value sets. The use of array theories impacts the completeness of SAGE, which was proven complete only for programs whose memory allocations are independent of their inputs. We are unaware of any completeness results regarding PEX, but we suspect that a proof would require the same qualifications as SAGE.

Several separation logic solvers have been proven to be sound and complete for heaps with linked lists~\cite{Navarro:2011,Cook:2011,Berdine:2005}, trees~\cite{Piskac:2014}, or data structures satisfying user-supplied invariants~\cite{Brotherston:2014}. Separation logic solvers can also reason about entailment, which is presently beyond the scope of~\symtxt{}. However,~\symtxt{} is sound and complete without restriction on data structures, and requires no explicit invariants.

>>>>

%DSE
A number of dynamic symbolic execution (\dsetxt{}) methods use some form 
of symbolic heap representation, including PEX~\cite{Tillmann:2008} and SAGE~\cite{Elkarablieh:2009}. These~\dsetxt{} methods have shown a high degree of utility in practical applications with a wide variety of real-world programs. PEX and SAGE use array theories to represent program state instead of guarded value sets.
SAGE has been proven complete for programs whose memory allocations are independent of their inputs. This work is complementary to PEX and SAGE, and we believe could be leveraged to further improve those tools.

Several separation logic solvers have been proven to be sound and complete for heaps with linked lists~\cite{Navarro:2011,Cook:2011,Berdine:2005}, trees~\cite{Piskac:2014}, or data structures satisfying user-supplied invariants~\cite{Brotherston:2014}. Separation logic solvers can also reason about entailment which is a subject of future work for symbolic initialization. Solutions in separation logic do not lend themselves to test case generation is  goal in this work.
